Ceph Parallel File System Evaluation Report

### 2013-08-30 introduction.tex
integrating sage's text
there are two missing references

Ceph\cite{Weil:2006:Ceph} originated from Sage Weil's PhD research at UC Santa
Cruz at 2007 and it was designed to be a reliable, scalable fault-tolerant
parallel file system.  Since then, Ceph has been open-sourced and Inktank is
now the major developer behind it.  In comparison to other parallel file
systems, Ceph has a number of distinctive features:

\begin{itemize}

@@

\end{itemize}

>>>>

Ceph\cite{Weil:2006:Ceph} is a distributed storage system designed for
scalability, reliability, and performance.  The system is based on a
distributed object storage service called RADOS (reliable autonomic distributed
object store) that manages the distribution, replication, and migration of
objects.  On top of that reliable storage abstraction Ceph builds a range of
services, including a block storage abstraction (RBD, or rados block device)
and a cache-coherent distributed file system (CephFS).

Data objects are distributed across storage daemons (ceph-osd) using
CRUSH\cite{crush}, a deterministic hashing function that allows administrators
to define flexible placement policies over a hierarchical cluster structure
(e.g., disks, hosts, racks, rows, datacenters).  Because the location of
objects can be calculated based on the object identifier and cluster layout
(similar to consistent hashing~\cite{..}), there is no need for a metadata
index or server for the RADOS object store. Further, because CRUSH provides an
authoritative view of data placement, storage daemons can coordinate directly
to handle data replications, recovery, or object migratation in the face of
failure or cluster topology changes.  A small cluster of monitors (ceph-mon
daemons) use Paxos to provide consensus on the current cluster layout, but do
not need to explicitly coordinate migration or recovery activities.

CephFS builds a distributed cache-coherent file system on top of the object
storage service provided by RADOS.  Files are striped over objects stored and
replicated by RADOS, while a separate cluster of metadata servers (ceph-mds
daemons) manage the file system namespace and coordinate client access to
files.

Ceph metadata servers store all metadata in RADOS object, which provides a
shared, highly-available, and reliable storage backend.  Unlike many other
distributed file system architectures, Ceph also embeds inodes inside
directories in the common case, allowing entire directories to read from RADOS
into the metadata server cache or prefetched into the client cache using a
single request.

Client hosts that mount the file system communicate with one or more metadata
servers to traverse the namespace but perform file IO by reading and writing
directly to RADOS objects that contain the file data.  The metadata server
cluster monitors the temperature of cached metadata and periodically adjusts
the distribution of the namespace across the MDS cluster by migrating
responsibility for arbitrary subtrees of the hierarchy between a dynamic pool
of active ceph-mds daemons.  This dynamic subtree partitioning~\cite{..}
strategy is both adaptive and highly scalable, allowing additional metadata
server daemons to be added or removed at any time, making it ideally suited
both for large-scale workloads with bursty workloads or general purpose
clusters whose workloads grow or contract over time.

In comparison to other parallel file
systems, Ceph has a number of distinctive features:

\begin{comment}
\begin{itemize}

@@

\end{itemize}
\end{comment}
